Coherent optical creation of a single molecule -- Supplemental material

### 2021-03-02 sm.tex
Whitespace and regenerate PDF
Fix reference styles and fix unicode/quote in references titles
Update on Overleaf.

\documentclass[aps,secnumarabic,amsmath,amssymb,10pt,superscriptaddress]{revtex4}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{color}
\usepackage{graphics}
\usepackage[pdftex]{graphicx}
\usepackage[utf8x]{inputenc}
\usepackage[colorlinks=true]{hyperref}
\usepackage{listings}
\usepackage{braket}
\usepackage{xcolor}
\newcommand\jmh[1]{{\color{magenta} #1}}

@@

% Add S1 to bibliography
\bibliographystyle{apsrev4-2}
\renewcommand*{\citenumfont}[1]{S#1}
\renewcommand*{\bibnumfmt}[1]{[S#1]}

@@

The state that we ultimately chose as the target state for Raman transfer is the least-bound
$(F,M_F)=(5,5)$ sublevel with $(f_{\rm Na},f_{\rm Cs}) = (2,3)$, which was predicted at a binding
energy 763 MHz below the $(f_{\rm Na},f_{\rm Cs}) = (2,3)$ threshold. As described in the text, it
was subsequently located experimentally at a binding energy of 770.57150(9) MHz.

@@

\section{Excited Molecular States} \label{sm:excited_states}
To obtain a full calculation for the expected Raman Rabi frequency, light shift and scattering, we need to account for all the excited molecular states.
The lowest eight excited molecular potentials in NaCs asymptote to the dissociation limit of Na 3S + Cs 6P.
These eight potentials can be written in the Hund's case (a) basis as $ \mathrm{c^3\Sigma^+_{\Omega = 0^-},c^3\Sigma^+_{\Omega = 1}, b^3\Pi_{\Omega = 0^-}, b^3\Pi_{\Omega = 0^+}, b^3\Pi_{\Omega = 1}, b^3\Pi_{\Omega = 2}, B^1\Pi_{\Omega = 1}, A^1\Sigma^+_{\Omega = 0^+}}$ \cite{Korek2007}.
Due to spin-orbit coupling, especially large in Cs, the excited molecular states are mixed, containing components in multiple potentials.
Fortunately, single-channel potential energy curves for $\mathrm{c^3\Sigma^+_1}$ and $  B^1\Pi_1 $ have been experimentally determined, and are predictive across the entire energy range of the potential \cite{Grochola2010, Grochola2011, Liu2017}.
Since there is only one $ \Omega = 2$ potential at this dissociation limit, a single-channel potential has been determined for $ b^3\Pi_2$ as well \cite{Zabawa2012}.
Unfortunately, single-channel potentials for the other electronic states do not exist.
A deperturbation analysis was required for states belonging to the mixed $\mathrm{A-b}$ complex,
and the fitted potentials and spin-orbit coupling coefficients are only accurate within the energy range of the measured experimental data \cite{Zaharova2009}.
Since our experiment attempts to work in a regime where the predominant Raman coupling comes from the $v' = 0$ state of $ \mathrm{c^3\Sigma^+_1} $,
the contribution of the other seven potentials is mainly to a background that is nearly detuning independent.
Thus, for computational ease, we use the diabatic potentials for $ \mathrm{b^3\Pi_{0}, b^3\Pi_{1}} $ and $ \mathrm{A^1\Sigma^+_{0^+}}$.
%and remove the states nearest to the $ v' = 0$ state of $ \mathrm{c^3\Sigma^+_1} $.
Lastly, to our knowledge, no potential fit to experimental data exists for the $ c^3\Sigma^+_{0^-}$ state. Assuming that its contribution is only to the background, as an approximation, we simply double the contribution of all states except $v' = 0$ from $ c^3\Sigma^+_1$.

>>>>

\documentclass[aps,prx,secnumarabic,amsmath,amssymb,10pt,superscriptaddress]{revtex4-2}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{color}
\usepackage{graphics}
\usepackage[pdftex]{graphicx}
\usepackage[utf8x]{inputenc}
\usepackage[colorlinks=true]{hyperref}
\usepackage{listings}
\usepackage{braket}
\usepackage{xcolor}
\newcommand\jmh[1]{{\color{magenta} #1}}

@@

% Add S1 to bibliography
\renewcommand*{\citenumfont}[1]{S#1}
\renewcommand*{\bibnumfmt}[1]{[S#1]}

@@

The state that we ultimately chose as the target state for Raman transfer is the least-bound
$(F,M_F)=(5,5)$ sublevel with $(f_{\rm Na},f_{\rm Cs}) = (2,3)$, which was predicted at a binding
energy 763 MHz below the $(f_{\rm Na},f_{\rm Cs}) = (2,3)$ threshold. As described in the text, it
was subsequently located experimentally at a binding energy of $ 770.1969(2) \mathrm{MHz} $ at $ 8.83(2) \mathrm{G} $.

@@

\section{Excited Molecular States} \label{sm:excited_states}
To obtain a full calculation for the expected Raman Rabi frequency, light shift and scattering, we need to account for all the excited molecular states.
The lowest eight excited molecular potentials in NaCs asymptote to the dissociation limit of Na 3S + Cs 6P.
These eight potentials can be written in the Hund's case (a) basis as $ \mathrm{c^3\Sigma^+_{\Omega = 0^-},c^3\Sigma^+_{\Omega = 1}, b^3\Pi_{\Omega = 0^-}, b^3\Pi_{\Omega = 0^+}, b^3\Pi_{\Omega = 1}, b^3\Pi_{\Omega = 2}, B^1\Pi_{\Omega = 1}, A^1\Sigma^+_{\Omega = 0^+}}$ \cite{Korek2007}.
Due to spin-orbit coupling, especially large in Cs, the excited molecular states are mixed, containing components in multiple potentials.
Fortunately, single-channel potential energy curves for $\mathrm{c^3\Sigma^+_1}$ and $  B^1\Pi_1 $ have been experimentally determined, and are predictive across the entire energy range of the potential \cite{Grochola2010, Grochola2011, Liu2017}.
Since there is only one $ \Omega = 2$ potential at this dissociation limit, a single-channel potential has been determined for $ b^3\Pi_2$ as well \cite{Zabawa2012}.
Unfortunately, single-channel potentials for the other electronic states do not exist.
A deperturbation analysis was required for states belonging to the mixed $\mathrm{A-b}$ complex,
and the fitted potentials and spin-orbit coupling coefficients are only accurate within the energy range of the measured experimental data \cite{Zaharova2009}.
Since our experiment attempts to work in a regime where the predominant Raman coupling comes from the $v' = 0$ state of $ \mathrm{c^3\Sigma^+_1} $,
the contribution of the other seven potentials is mainly to a background that is nearly detuning independent.
Thus, for computational ease, we use the diabatic potentials for $ \mathrm{b^3\Pi_{0}, b^3\Pi_{1}} $ and $ \mathrm{A^1\Sigma^+_{0^+}}$.
% and remove the states nearest to the $ v' = 0$ state of $ \mathrm{c^3\Sigma^+_1} $.
Lastly, to our knowledge, no potential fit to experimental data exists for the $ c^3\Sigma^+_{0^-}$ state. Assuming that its contribution is only to the background, as an approximation, we simply double the contribution of all states except $v' = 0$ from $ c^3\Sigma^+_1$.
